RELATION BETWEEN STAR FORMATION RATE, GAS MASS AND STELLAR MASS IN THE ANDROMEDA GALAXY

### 2015-02-25 draft3.tex
with final tables

\documentclass[useAMS,usenatbib]{mn2e}
%\usepackage{geometry}[left=1.5in, right=1in, bottom=1in, top=1in]
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{natbib}
\bibliographystyle{aas}
\usepackage{amsmath}
\usepackage{times}
\usepackage{float}

@@

\begin{table}
\caption{Data used in this study.}
\label{table:data}
\begin{tabular}{@{}lccc}
\hline\hline
Wavelength & FWHM & Telescope
& Ref. \\
\hlin
%500 \um & 36\arcsec & $Herschel$ & \cite{Fritz12} \\
%350 \um & 24\arcsec.5 & $Herschel$ & \cite{Fritz12} \\
%250 \um & 18\arcsec.2 & $Herschel$ & \cite{Fritz12} \\
2250~\AA & 6\arcsec & GALEX & \cite{Martin05}\\ %:PB: GALEX, KPNO, IRAM should not be in $$
1550~\AA & 4\arcsec.5 & GALEX & \cite{Martin05}\\ %PB (they are abbreviations)
6570~\AA  & 1\arcsec & KPNO& \cite{Massey07}\\
3.6~\um & 1\arcsec.7 & \Spitzer & \cite{Barmby06} \\ %PB: write {\it Spitzer}, {\it Herschel}
4.5~\um & 1\arcsec.7 & \Spitzer & \cite{Barmby06} \\ %PB because those are both missions and names
8~\um & 1\arcsec.9 & \Spitzer & \cite{Barmby06} \\ % PB: of people - italics means the mission, not
24~\um & 6\arcsec & \Spitzer & \cite{Gordon06} \\ %PB: the person
70~\um & 18\arcsec & \Spitzer & \cite{Gordon06} \\
160~\um & 12\arcsec & \Herschel & \cite{Fritz12} \\
2.6~mm & 23\arcsec & IRAM 30-m & \cite{Nieten06}\\
21~m & 60\arcsec \times \ 90\arcsec & DRAO & \cite{Chemin09}\\
\hline
\end{tabular}
\end{table}

@@

%PB: I like this figure! Looks nice.
\begin{figure*}
        \centering
        \begin{subfigure}\\(a){}
                \includegraphics[width=164mm]{sfr_fuv.eps}
                %\caption{A gull}

               \label{fig:sfr_halpha}
        \end{subfigure}
        \begin{subfigure}\\(b){}
                \includegraphics[width=164mm]{sfr_halpha.eps}
                %\caption{A gull}

               \label{fig:sfr_halpha}
        \end{subfigure}
        \begin{subfigure}\\(c){}
                \includegraphics[width=164mm]{sfr_fir.eps}
                %\caption{A tiger}

                \label{fig:sfr_fir_small}
        \end{subfigure}
         \quad
               \caption{SFR map from a combination of FUV + 24\um emission (top), \halpha and 24\um emission (middle), and total infrared emission (bottom)}
\label{fig:sfrs}
\end{figure*}
%----------------------------------------------------------------------------------------
%ISM
%----------------------------------------------------------------------------------------
\section{Interstellar Medium}
%----------------------------------------------------------------------------------------
%Direct Measurement of the Gas Mass
%----------------------------------------------------------------------------------------
%\subsubsection{Direct Measurement of the Gas Mass}

@@

\begin{figure*}
\centering
\includegraphics{ks_tot_compt.png}
\caption{The result from fitting the Kennicutt-Schmidt law on data from whole galaxy using pixel by pixel method. Plots have a different pixel size. Each point in the plots with the surface density of H2 as a tracer of gas mass represents regions $~$ Kpc and points in plots with surface density of HI or total gas mass, represeents region in $~$Kpc.} 
\label{fig:ks,all}
\end{figure*}

@@

% \begin{figure*}
% %\centering
% \includegraphics{ks_8kpc_all.png}
% \caption{same as figure ~\ref{fig:ks,tot}, but for the regions with R less than 8$\kpc$ }
% \label{fig:ks,8}
% \end{figure*}

% \begin{figure*}
% %\centering
% \includegraphics{ks_8kpc_18kpc_all.png}
% \caption{same as figure ~\ref{fig:ks,tot}, but for the regions with $8\kpc < $R $< 18\kpc$}
% \label{fig:ks,18}
% \end{figure*}

% \begin{figure*}
% %\centering
% \includegraphics{ks_18kpc_25kpc_all.png}
% \caption{same as figure ~\ref{fig:ks,tot}, but for the regions with $18\kpc <$ R $\la 25\kpc$}
% \label{fig:ks,25}
% \end{figure*}

\begin{figure*}
\includegraphics[width=164mm]{c3d_all_ks_regs.png}
\caption{same as figure ~\ref{fig:ks,tot}, but in this figure we separated pixels from different regions in galaxy by their colours. The regions with R less than 8$\kpc$, $8\kpc < $R $< 18\kpc$, and $18\kpc <$ R $\la 25\kpc$ are shown in red, green and blue, respectively.}
\label{fig:ks,regs}
\end{figure*}

@@

\begin{figure}
	\begin{subfigure}\\(a){}
  	\left
	\includegraphics[width=80mm]{es_tot_fuv_vs_h2.png}
 	\end{subfigure}%

	 \begin{subfigure}\\(b){}
	\right
	\includegraphics[width=80mm]{es_tot_fir_vs_h2.png}
 	\end{subfigure}

	 \begin{subfigure}\\(c){}
 	\left
	\includegraphics[width=80mm]{es_tot_fir_vs_hi.png}
 	\end{subfigure}

 	\begin{subfigure}\\(d){}
   	\right
	\includegraphics[width=80mm]{es_tot_fuv_vs_hi.png}
 	\end{subfigure}

 	\begin{subfigure}\\(e){}
   	\left
	\includegraphics[width=80mm]{es_tot_fir_vs_tot.png}
 	\end{subfigure}

 	\begin{subfigure}\\(f){}
   	\right
	\includegraphics[width=80mm]{es_tot_fuv_vs_tot.png}
	 \end{subfigure}

\caption{The result from fitting the extended Schmidt law on data from whole galaxy using pixel by pixel method. Plots have a different pixel size. Each point in the plots with the surface density of H2 as a tracer of gas mass represents regions $~$ Kpc and points in plots with surface density of HI or total gas mass, represeents region in $~$Kpc.}
%PB: explain a little more here what you mean by "plots have different pixel size", or refer to the relevant text section.
   \label{fig:es,all}
 \end{figure}

@@

\begin{figure*}
\centering
\includegraphics[width=162mm]{c3d_fir_hi.png}
\caption{Fitting result from the SFR(TIR) vs HI.}
\label{fig:es,regs,fir,hi}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[width=162mm]{c3d_fir_h2.png}
\caption{Fitting result from the SFR(TIR) vs H$_{2}$.}
\label{fig:es,regs,fir,h2}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[width=162mm]{c3d_fuv_hi.png}
\caption{Fitting result from the SFR(FUV + 24 $\mu$m) vs HI.}
\label{fig:es,regs,fuv,hi}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[width=162mm]{c3d_fuv_h2.png}
\caption{Fitting result from the SFR(FUV + 24 $\mu$m) vs H$_{2}$.}
\label{fig:es,regs,fuv,h2}
\end{figure*}

%PB: in these tables, having the numbers all in the same format  (eg with or without the 1e-2
%PB type notation) makes it easier to compare. Negative numbers should be written $-x.xx$.
%THE REST WOULD BE THE comparison of the results:
\begin{table*}
\caption{global fitting parameters of the SF laws from applying the Bayesian fitting.}
\label{table:sf-laws_all}
\begin{tabular}{@{}lccccccccccc}
\hline\hline
SFR Tracer& Gas Tracer & N & \sigma$_N$ & $\log$(const$_{KS}$)& \nprime & $\sigma_{\eqnprime}$ & \beta& \sigma$_\beta$&$\log$(const$_{ES}$)&$\sigma_{scatter}$ \\
\hline
FIR&H$_2$only&1.03 &9.47e-3 &-8.92 &0.95 &9.78e-3 &0.34 &4.25 &-9.57 & & &
FIR&HI only& 1.15&9.13e-3 &-9.87 &0.77 &8.84e-3 &0.74 &4.58e-3 &-10.71 & & &
FIR&Total gas&0.81 &6.27e-3 &-9.84 &0.30 &8.73e-3 &0.60 & 1.21e-2&-10.40 & & &
FUV + 24\um &H$_2$only& 1.15&1.16e-2 &-9.28 &1.10 &1.21e-2 &0.25 &4.88e-3 &-9.76 & & &
FUV + 24\um &HI only& 1.21&9.13e-3 &-9.87 &0.80 &7.33e-3 &0.60 &4.02e-3 &-10.70 & & &
FUV + 24\um &Total gas&0.78& 4.67e-3&-10.05 &0.80 &7.35e-3 &0.60 &3.98e-3 &-10.70 & & &
\hline
\end{tabular}
\end{table*}

\begin{table*}
\caption{Fitting parameters of the SF laws from applying the Bayesian fitting on regions with R less than 8$\kpc$ .}
\label{table:sf-laws_8}
\begin{tabular}{@{}lccccccccccc}
\hline\hline
SFR Tracer& Gas Tracer & N & \sigma$_N$ & $\log$(const$_{KS}$)& \nprime & $\sigma_{\eqnprime}$ & \beta& \sigma$_\beta$&$\log$(const$_{ES}$)&$\sigma_{scatter}$ \\
\hline
FIR&H$_2$only&0.96 &1.48e-2 &-8.95 &0.88 &1.48e-2 &0.30 &6.11e-3 &-9.54 & & &
FIR&HI only&0.79 &0.03 &-9.89 &0.47 &0.30 &1.57 &0.28 &-12.11 & & &
FIR&Total gas&1.00 &0.03 &-10.12 &0.63 &0.03 &0.53 &0.08 &-10.62 & & &
FUV + 24\um &H$_2$only&1.04 &1.84e-2 &-9.29 &1.00 &1.85e-2 &0.18 &7.17e-3 &-9.65 & & &
FUV + 24\um &HI only&0.68 &0.02 &-10.03 &0.92 &0.06 &0.42 &0.04 &-10.50 & & &
FUV + 24\um &Total gas&0.87 &0.026 &-10.12 &0.75 &0.03 &0.16 &0.04 &-10.28 & & &
\hline
\end{tabular}
\end{table*}

\begin{table*}
\caption{Fitting parameters of the SF laws from applying the Bayesian fitting on regions with $8\kpc < $R $< 18\kpc$.}
\label{table:sf-laws_18}
\begin{tabular}{@{}lccccccccccc}
\hline\hline
SFR Tracer& Gas Tracer & N & \sigma$_N$ & $\log$(const$_{KS}$)& \nprime & $\sigma_{\eqnprime}$ & \beta& \sigma$_\beta$&$\log$(const$_{ES}$)&$\sigma_{scatter}$ \\
\hline
FIR&H$_2$only&1.08 &1.26e-2 &-8.90 &1.00 &1.29e-2 &0.40 &5.74e-3 &-9.66 & & &
FIR&HI only&1.09 &2.64e-2 &-8.93 &0.77 &0.025 &0.75 &0.01 &-10.71 & & &
FIR&Total gas&0.75 &0.02 &-10.02 &0.47 &0.01 &0.55 &0.01 &-10.53 & & &
FUV + 24\um &H$_2$only&1.21 &1.53e-2 &-9.27 &1.15 &1.58e-2 &0.33 &6.57e-3 &-9.66 & & &
FUV + 24\um &HI only&1.18 &2.89e-2 &-9.81 &0.81 &2.08e-2 &0.61 &1.12e-2 &-10.73 & & &
FUV + 24\um &Total gas&0.71 &1.34e-2 &-10.02 &0.44 &0.01 &0.45 &0.01 &-10.58 & & &
\hline
\end{tabular}
\end{table*}

\begin{table*}
\caption{Fitting parameters of the SF laws from applying the Bayesian fitting on regions with $18\kpc <$ R $\la 25\kpc$.}
\label{table:sf-laws_25}
\begin{tabular}{@{}lccccccccccc}
\hline\hline
SFR Tracer& Gas Tracer & N & \sigma$_N$ & $\log$(const$_{KS}$)&$\sigma_{scatter,KS}$& \nprime & $\sigma_{\eqnprime}$ & \beta& \sigma$_\beta$&$\log$(const$_{ES}$)&$\sigma_{scatter,ES}$ \\
\hline
FIR&H$_2$only&1.57 &0.26 &-8.80 &6.03e+2&0.97 &0.20 &1.19 &0.1 &-10.94 &6.44e+2 & 
FIR&HI only&1.17 &0.05 &-9.65 &3.60e+2&0.76 &0.03 &0.75 &0.01 &-10.72 &3.96e+2 & 
FIR&Total gas&0.84 &0.02 &-9.85 &3.13e+2&0.50 &0.01 &0.48 &0.01 &-10.62 & 3.61e+2& 
FUV + 24\um &H$_2$only&1.87 &0.30 &-9.14 &5.72e+2&1.33 &0.29 &1.38 &0.12 &-11.65 & 5.80e+2& 
FUV + 24\um &HI only&1.22 &0.03 &-9.22 &2.75e+2&0.79 &0.02 &0.62 &0.01 &-10.73 & 3.82e+2&
FUV + 24\um &Total gas&0.81 &1.59 &-10.06 &3.80e+2&0.42 &0.01 &0.52 &0.02 &-10.68 &3.53e+2 & 
\hline
\end{tabular}
\end{table*}

@@

Figures ~\ref{fig:fit,params,fir} and ~\ref{fig:fit,params,fuv} show results of the fitting parameters for SFR(TIR) and SFR(FUV+24\um) in three different regions. In case of Total gas for the K-S law, there is a sublinear retaliation between SFR and gas mass, in global case and all regions.This result is significatly lower than results from \cite{Ford13}. But it is similar to prediction of the \cite{Shetty13}, which argued that using the hierarchical Bayesian fit leads to power index N lower than other works. 
%PB: more detailed comparison to Ford here: what values did he find, are these significantly different from yours?
%PB: Also compare to Shetty's results: what did he find for other galaxies and are your results compatible with those?

@@

\begin{figure*}
\centering
\includegraphics[width=162mm]{fir_res2.png}
\caption{Fitting parameters for SFR(TIR) }
\label{fig:fir,params,fir}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[width=162mm]{fuv_res.png}
\caption{Fitting parameters for SFR(FUV + 24\um ) }
\label{fig:fir,params,fuv}
\end{figure*}

>>>>

\documentclass[useAMS,usenatbib]{mn2e}
%\usepackage{geometry}[left=1.5in, right=1in, bottom=1in, top=1in]
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{natbib}
\bibliographystyle{aas}
\usepackage{amsmath}
\usepackage{times}
\usepackage{float}
\usepackage{caption}
%\usepackage[caption=false]{subfig}
\usepackage{subcaption}
\usepackage{multirow}

@@

\begin{table}
\caption{Data used in this study.}
\label{table:data}
\begin{tabular}{@{}lccc}
\hline\hline
Wavelength & FWHM & Telescope
& Ref. \\
\hline
%500 \um & 36\arcsec & $Herschel$ & \cite{Fritz12} \\
%350 \um & 24\arcsec.5 & $Herschel$ & \cite{Fritz12} \\
%250 \um & 18\arcsec.2 & $Herschel$ & \cite{Fritz12} \\
2250~\AA & 6\arcsec & GALEX & \cite{Martin05}\\ %:PB: GALEX, KPNO, IRAM should not be in $$
1550~\AA & 4\arcsec.5 & GALEX & \cite{Martin05}\\ %PB (they are abbreviations)
6570~\AA  & 1\arcsec & KPNO& \cite{Massey07}\\
3.6~\um & 1\arcsec.7 & \Spitzer & \cite{Barmby06} \\ %PB: write {\it Spitzer}, {\it Herschel}
4.5~\um & 1\arcsec.7 & \Spitzer & \cite{Barmby06} \\ %PB because those are both missions and names
8~\um & 1\arcsec.9 & \Spitzer & \cite{Barmby06} \\ % PB: of people - italics means the mission, not
24~\um & 6\arcsec & \Spitzer & \cite{Gordon06} \\ %PB: the person
70~\um & 18\arcsec & \Spitzer & \cite{Gordon06} \\
160~\um & 12\arcsec & \Herschel & \cite{Fritz12} \\
2.6~mm & 23\arcsec & IRAM 30-m & \cite{Nieten06}\\
21~m & 60\arcsec \times \ 90\arcsec & DRAO & \cite{Chemin09}\\
\hline
\end{tabular}
\end{table}

@@

%PB: I like this figure! Looks nice.

\begin{figure*}
    \centering
    \begin{subfigure}[b]{1\textwidth}
        \centering
        \includegraphics[width=164mm]{sfr_fuv.eps}
        \caption{SFR,FUV+24\um}
        \label{fig:sfr,fuv}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{1\textwidth}
        \centering
        \includegraphics[width=164mm]{sfr_halpha.eps}
        \caption{SFR,H$_{\alpha}$}
        \label{fig:sfr_halpha}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{1\textwidth}
        \centering
        \includegraphics[width=164mm]{sfr_fir.eps}
        \caption{SFR,TIR}
        \label{fig:sfr,fir}
    \end{subfigure}
    \caption{SFR map from a combination of FUV + 24\um emission (top), \halpha and 24\um emission (middle), and total infrared emission (bottom)}
    \label{fig:sfrs}
\end{figure*}
%----------------------------------------------------------------------------------------
%ISM
%----------------------------------------------------------------------------------------
\section{Interstellar Medium}
%----------------------------------------------------------------------------------------
%Direct Measurement of the Gas Mass
%----------------------------------------------------------------------------------------
%\subsubsection{Direct Measurement of the Gas Mass}

@@

\begin{figure*}
\centering
\includegraphics[width=164mm]{ks_all_1.png}
\caption{The result from fitting the Kennicutt-Schmidt law on data from whole galaxy using pixel by pixel method. Plots have a different pixel size. Each point in the plots with the surface density of H2 as a tracer of gas mass represents regions $~$ Kpc and points in plots with surface density of HI or total gas mass, represeents region in $~$Kpc.} 
\label{fig:ks,all}
\end{figure*}

@@

\begin{figure*}
\includegraphics[width=164mm]{c3d_all_ks_regs_1.png}
\caption{same as figure ~\ref{fig:ks,all}, but in this figure we separated pixels from different regions in galaxy by their colours. The regions with R less than 8$\kpc$, $8\kpc < $R $< 18\kpc$, and $18\kpc <$ R $\la 25\kpc$ are shown in red, green and blue, respectively.}
\label{fig:ks,regs}
\end{figure*}

@@

\begin{figure*}
    \centering
    \begin{subfigure}[b]{0.3\textwidth}
        \centering
        \includegraphics[width=\textwidth]{es_tot_fir_vs_h2.png}
        \caption{SFR,TIR vs surface density of H$_2$}
        \label{fig:es,all,fir,h2}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.3\textwidth}
        \centering
        \includegraphics[width=\textwidth]{es_tot_fuv_vs_h2.png}
        \caption{SFR,FUV+24\um vs surface density of H$_2$}
        \label{fig:es,all,fuv,h2}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=\textwidth]{es_tot_fir_vs_hi.png}
        \caption{SFR,TIR vs surface density of HI}
        \label{fig:es,all,fir,hi}
    \end{subfigure}
     \centering
    \begin{subfigure}[b]{0.3\textwidth}
        \centering
        \includegraphics[width=\textwidth]{es_tot_fuv_vs_hi.png}
        \caption{SFR,FUV+24\um vs surface density of HI}
        \label{fig:es,all,fuv,hi}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.3\textwidth}
        \centering
        \includegraphics[width=\textwidth]{es_tot_fir_vs_tot.png}
        \caption{SFR,TIR vs surface density of total gas}
        \label{fig:es,all,fir,tot}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.3\textwidth}
        \centering
        \includegraphics[width=\textwidth]{es_tot_fuv_vs_tot.png}
        \caption{SFR,FUV+24\um vs surface density of total gas}
        \label{fig:es,all,fuv,tot}
    \end{subfigure}
    \caption{The result from fitting the extended Schmidt law on data from whole galaxy using pixel by pixel method. Plots show SFR vs surface density of gas, and z-axis is surface density of the stellar mass. Each figure shows different combination of the SFR tracer and gas mass tracer results. Plots have a different pixel size. Each point in the plots with the surface density of H2 as a tracer of gas mass represents regions $\sim$30~Kpc and points in plots with surface density of HI or total gas mass, represents region in $\sim$155~Kpc.}
    \label{fig:es,all}
\end{figure*}

% \begin{figure*}
% \centering
% \includegraphics[width=162mm]{c3d_fir_h2.png}
% \caption{Fitting result from the SFR(TIR) vs H$_{2}$.}
% \label{fig:es,regs,fir,h2}
% \end{figure*}

% \begin{figure*}
% \centering
% \includegraphics[width=162mm]{c3d_fuv_h2.png}
% \caption{Fitting result from the SFR(FUV + 24 $\mu$m) vs H$_{2}$.}
% \label{fig:es,regs,fuv,h2}
% \end{figure*}

% \begin{figure*}
% \centering
% \includegraphics[width=162mm]{c3d_fir_hi.png}
% \caption{Fitting result from the SFR(TIR) vs HI.}
% \label{fig:es,regs,fir,hi}
% \end{figure*}

% \begin{figure*}
% \centering
% \includegraphics[width=162mm]{c3d_fuv_hi.png}
% \caption{Fitting result from the SFR(FUV + 24 $\mu$m) vs HI.}
% \label{fig:es,regs,fuv,hi}
% \end{figure*}

@@

\begin{table*}
\caption{Fitting parameters of the SF laws from applying the Bayesian.}
\label{table:res}
\begin{tabular}{||cc||cccrcccccr}
\hline\hline
\multicolumn{1}{||c||}{\multirow{1}{*}{Region}} & SFR Tracer& Gas Tracer & N & $\sigma_N$ & A & \nprime & $\sigma_{\eqnprime}$ & $\beta$ & $\sigma_\beta$ & A$^\prime$& \\
\hline
\multicolumn{1}{||c||}{\multirow{6}{*}{Global case}} & TIR & H$_2$ only & 1.03 & 9.47e-3  & -8.92  & 0.95 & 9.77e-3 & 0.34 & 4.25e-3 & -9.57  \\
 & TIR         & HI only    & 1.15 & 1.47e-2 & $-9.63$  & 0.77 & 8.84e-3 & 0.75 & 4.58e-3 & $-10.71$ \\
 & TIR         & Total gas  & 0.81 & 6.27e-3 & $-9.84$  & 0.50 & 4.49e-3 & 0.55 & 4.57e-3 & $-10.53$\\
 & FUV + 24\um & H$_2$ only & 1.15 & 1.16e-2 & $-9.28$  & 1.09 & 1.21e-2 & 0.25 & 4.88e-3 & $-9.76$  \\
 & FUV + 24\um & HI only    & 1.21 & 9.13e-3 & $-9.87$  & 0.81 & 7.34e-3 & 0.60 & 4.10e-3 & $-10.70$ \\
 & FUV + 24\um & Total gas  & 0.78 & 4.67e-3 & $-10.06$ & 0.48 & 4.61e-3 & 0.45 & 4.69e-3 & $-10.57$ \\
\hline
\multicolumn{1}{||c||}{\multirow{6}{*}{R$< 8\kpc$}}& TIR & H$_2$ only & 0.96 & 1.48e-2 & -8.95  & 0.88 & 1.49e-2 & 0.30 & 6.11e-3 & -9.54  \\
 & TIR         & HI only    & 1.52 & 7.73e-2  & -9.91  & 1.00 & 7.27e-2  & 0.60 & 4.22e-2  & -10.60 \\
 & TIR         & Total gas  & 1.00 & 3.51e-2  & -10.04 & 0.63 & 3.47e-2  & 0.53 & 7.57e-2  & -10.63 \\
 & FUV + 24\um & H$_2$ only & 1.04 & 1.84e-2 & -9.29  & 1.00 & 1.85e-2 & 0.18 & 7.17e-3 & -9.64  \\
 & FUV + 24\um & HI only    & 1.28 & 4.73e-2  & -10.00 & 0.93 & 5.68e-2  & 0.42 & 3.81e-2  & -10.50 \\
 & FUV + 24\um & Total gas  & 0.88 & 2.59e-2  & -10.12 & 0.75 & 3.53e-2  & 0.16 & 3.93e-2  & -10.28 \\
\hline
\multicolumn{1}{||c||}{\multirow{6}{*}{$8\kpc < $R $< 18\kpc$}} & TIR & H$_2$ only & 1.08 & 1.26e-2 & -8.90  & 1.00 & 1.29e-2 & 0.40 & 5.74e-3 & -9.66  \\
 & TIR         & HI only    & 1.09 & 4.50e-2 & -9.54  & 0.77 & 2.52e-2  & 0.75 & 1.26e-2  & -10.71 \\
 & TIR         & Total gas  & 0.75 & 1.76e-2  & -9.81  & 0.47 & 1.18e-2  & 0.55 & 1.24e-2  & -10.53 \\
 & FUV + 24\um & H$_2$ only & 1.21 & 1.53e-2 & -9.27  & 1.15 & 1.57e-2 & 0.33 & 6.57e-3 & -9.89  \\
 & FUV + 24\um & HI only    & 1.18 & 2.89e-2 & -9.81  & 0.81 & 2.08e-2 & 0.61 & 1.12e-2 & -10.73 \\
 & FUV + 24\um & Total gas  & 0.71 & 1.34e-2 & -9.81  & 0.44 & 1.18e-2  & 0.45 & 1.28e-2  & -10.58 \\
\hline
\multicolumn{1}{||c||}{\multirow{6}{*}{$18\kpc <$ R $\la 25\kpc$}}  & TIR & H$_2$ only & 1.57 & 2.63e-1  & -8.80  & 0.97 & 2.00e-1  & 1.19 & 1.01e-1  & -10.94 \\
 & TIR         & HI only    & 1.17 & 4.67e-2 & -9.65  & 0.76 & 2.82e-2 & 0.75 & 1.48e-2 & -10.72 \\
 & TIR         & Total gas  & 0.84 & 2.06e-2  & -9.85  & 0.52 & 1.45e-2  & 0.56 & 1.42e-2  & -10.56 \\
 & FUV + 24\um & H$_2$ only & 1.87 & 3.03e-1  & -9.15  & 1.33 & 2.95e-1  & 1.38 & 1.12e-1  & -11.65 \\
 & FUV + 24\um & HI only    & 1.22 & 2.96e-2 & -9.88  & 0.79 & 2.31e-2 & 0.62 & 1.28e-2 & -10.73 \\
 & FUV + 24\um & Total gas  & 0.81 & 1.59e-2 & -10.06 & 0.42 & 1.14e-2  & 0.52 & 2.06e-1  & -10.69 \\
 \hline
\end{tabular}
\end{table*}

@@

Table ~\ref{table:res} shows results of the fitting parameters for SFR(TIR) and SFR(FUV+24\um) in three different regions. In case of Total gas for the K-S law, there is a sublinear retaliation between SFR and gas mass, in global case and all regions.This result is significatly lower than results from \cite{Ford13}. But it is similar to prediction of the \cite{Shetty13}, which argued that using the hierarchical Bayesian fit leads to power index N lower than other works. 
%PB: more detailed comparison to Ford here: what values did he find, are these significantly different from yours?
%PB: Also compare to Shetty's results: what did he find for other galaxies and are your results compatible with those?

@@

% \begin{figure*}
% \centering
% \includegraphics[width=162mm]{fir_res2.png}
% \caption{Fitting parameters for SFR(TIR) }
% \label{fig:fit,params,fir}
% \end{figure*}

% \begin{figure*}
% \centering
% \includegraphics[width=162mm]{fuv_res.png}
% \caption{Fitting parameters for SFR(FUV + 24\um ) }
% \label{fig:fit,params,fuv}
% \end{figure*}
